### 2022-02-15 chapters/intro/intro.tex
relecture II

Coral reefs are among the most productive and biologically diverse ecosystems on Earth \citep{connell1978diversity, moberg1999ecological}. They supply food, income and coastal protection to vast numbers of people (Fig. \ref{intro:corals}). While they account for less than 0.5\% of the ocean floor \citep{spalding1997new}, they are home for almost a third of the marine biodiversity \citep{moberg1999ecological}. Reef-related fisheries account to up to 40\% of the total marine
fish landed value of some regions \citep{teh2013global} and hundreds of millions of people depend on coral reefs for their livelihood or part of their protein intake \citep{salvat1992coral,hoegh2019people}. Through calcification, corals are the backbone of a complex three-dimensional habitat that serves as spawning, breeding and feeding area for many species \citep{moberg1999ecological,rogers2014vulnerability}. This complex reef framework  dissipates most of incoming waves energy, protects shorelines from storms and floods, and prevents coastal erosion \citep{ferrario2014effectiveness,elliff2017coral}. Additionally, wave dissipation creates lagoon and sedimentary environment, providing favorable conditions for the growth of seagrass and mangrove ecosystems \citep{moberg1999ecological,guannel2016power}.

@@

The calcifying process of reef building corals heavily depends on their symbiosis with the microalgae zooxanthellae. These unicellular symbionts convert sunlight and carbon dioxide into organic carbon and oxygen, providing the corals with most of the energy needed to meet their metabolic demands \citep{muscatine1977reef}. However, adverse environmental conditions such as elevated sea surface temperature can cause damage to the mechanisms maintaining this association, resulting in the expulsion of the endosymbionts \citep{hoegh2007coral,van2022global}. This process, called bleaching, causes the coral to loose their pigmentation and reveals their underlying white skeleton \citep{baker2008climate}. Bleached corals are physiologically and nutritionally compromised, and prolonged bleaching over several months leads to high coral mortality \citep{hughes2018spatial}. Decline in coral health and cover pushes the reef ecosystem to a macroalgal-dominated state \citep{hughes2003climate,mumby2007thresholds}. Once a "tipping point" is exceeded, returning to a coral-dominated state becomes difficult \citep{mumby2007thresholds,graham2015predicting}.

Despite their importance, coral reefs have experienced a massive system-wide decline: it is estimated  that 50\% have already been severely damaged \citep{hoegh2019people}, and almost all could be lost under a 1.5$^\circ$C warming \citep{dixon2022future}. This global decline in live coral cover \citep{gardner2003long,pandolfi2003global,pandolfi2011projecting,perry2013caribbean,dietzel2021population} (Fig. \ref{intro:cover}) is caused by both global and local anthropogenic stressors. The main global stressors are climate change induced ocean warming and acidification \citep{dove2020ocean,figueiredo2021global,dixon2022future}. Ocean warming causes recurrent mass bleaching events at an increasing frequency \citep{connell199730, hughes2018spatial,van2022global}. Furthermore, thermal stress can increase the susceptibility of corals to disease, leading to an increase in the incidence of coral disease outbreaks \citep{harvell2002climate,bruno2007thermal,muller2012caribbean,howells2020annual}. Moreover, the increase of the concentration of atmospheric carbon dioxyde causes a decrease of the pH and carbonate concentration of seawater. As a result, coral calcification and growth decrease, which inhibits their capacity to build structurally complex habitats \citep{hoegh2007coral,albright2016reversal}. Local stressors are numerous and include pollution \citep{loya1980effects,van2011chemical}, coastal development and the associated sediment and wastewater fluxes \citep{erftemeijer2012environmental, cunning2019extensive}, nutrient run-off \citep{hughes2003climate,fabricius2005effects}, and overfishing of herbivorous species controlling algae growth \citep{jackson2001historical,shantz2020overfishing}.

@@

Due to the combined damages from of all these stressors, it is almost impossible to return reefs to their past configurations \citep{hughes2017coral}. Instead, the challenge is now to maintain the biological functions of coral reefs through quickly changing environmental conditions. This will require to rapidly address greenhouse gas emissions, as well as local actions to boost the capacity of coral reef ecosystems to survive climate change \citep{hughes2003climate,knowlton2008shifting,graham2015predicting,kleypas2021designing}. The aim of the present dissertation was therefore to use modeling tools to better understand the drivers of coral demise and hence inform such local actions to support ecosystem management in Florida, the third largest barrier reef of the world.

@@

The Florida Reef Tract (FRT) spans over approximately 577 km from the Dry Tortugas (DRTO) west of the Florida Keys to the St. Lucie Inlet in Martin County, constituting the third largest barrier reef in the world \citep{finkl2008shelf} (Fig. \ref{intro:frt}). These reefs harbor a rich Caribbean fauna, including more than 40 species of stony corals \citep{banks2008reef,jackson2014status}. The northern half-section of the FRT consists of relic, Holocene framework reefs and indurated sand ridges, divided into three shore-parallel reefs (inner, middle, outer) separated by sandy plains. Benthic cover is generally denser on the middle and outer reefs while the inner reef harbors some large patches of dense \textit{Acropora cervicornis}. The dominant reef builder is the bouldering \textit{Montastraea cavernosa} but living hard coral cover is fairly low (below 3\%)\citep{banks2008reef,walton2018impacts}. The southern half-section is a chain of limestone islands (the Keys) that extend from the southern tip of the Florida mainland southwest to the DRTO on the the boundary of the West Florida Shelf (WFS). The Upper Keys are remnants of ancient coral reefs and the Lower Keys are sand bars \citep{hoffmeister1968geology}. The DRTO are made of small circular reef banks whose coral populations are among the most preserved of the continental United States \citep{hine2008coral, kourafalou2018physical}. Moreover, they are believed to be important sources of recruitment for coral-reef fishes in the Florida Keys \citep{domeier2004potential}.

@@

Florida's Coral Reef (FCR) is of considerable importance to the economy of the state. \cite{johns2003socio} estimated the contribution of recreational users of natural and artificial reefs over the period June 2000 to May 2001 to have been US\$2.3 billions in sales and US\$1.1 billion in income. Moreover, recreational use of the reefs was evaluated to bring 36,500 full and part-time jobs. Focusing on natural reefs only, \cite{brander2013total} estimated the total coral reef values Florida to be US\$174 millions. However, this value might be strongly underestimated as non-use and indirect use values, such as support for coastal fisheries \citep{ault2006building} and coastal protection \citep{ferrario2014effectiveness} were not taken into account.

Nevertheless, FCR has been heavily impacted by the human activities of the major metropolitan area of greater Miami. These impacts include densely populated coastlines, large numbers of visitors, polluted terrestrial run-off and overfishing \citep{jackson2014status}. For example, dredging operations during the PortMiami Deep Dredge Project (PMDDP) was reported to have caused the death of $>$560,000 corals \citep{cunning2019extensive}. Florida's coral reefs have therefore declined significantly over the past decades due to anthropogenic stressors and numerous disease outbreaks \citep{gardner2003long, jackson2014status}. Populations of previously dominant reef-building acroporids almost totally disappeared throughout the Caribbean and Florida \citep{aronson2001white}, and coral cover dropped from 40 to 60\% in 1975 to $<$7\% in the Florida Keys \citep{jackson2014status} and $<$3\% in the northern section of the FRT \citep{walton2018impacts}. Furthermore, since 2014, many coral species have experienced widespread and severe decline caused by the ongoing outbreak of stony coral tissue loss disease (SCTLD). For instance, populations of \textit{M. cavernosa}, once one of the most abundant species of the FRT, decreased by 45\% in abundance between 2015 and 2016 \citep{walton2018impacts}.

@@

The aforementioned large-scale ocean circulation significantly impacts transport processes in the FRT. The modeling tools developed in this thesis should therefore be able to capture them accurately. Furthermore, as our objective is to model the dispersal of disease agents and sediments in a topologically complex coastal reef ecosystem, our modeling framework should also be able to capture small-scale ocean circulation features. For instance, small-scale flow features such as recirculation eddies around reefs and islands have been shown to strongly influence larval dispersal by increasing their local retention over the reefs \citep{figueiredo2013synthesizing}. Furthermore, accurately capturing the topography of coastal areas is critical when modeling storm conditions, as large wind waves generate strong currents, waves and storm surges in nearshore regions \citep{dietrich2010high, weisberg2006hurricane}. A reference ocean model of the FRT is the 3D HYbrid Coordinate Ocean Model (HYCOM, \citealp{chassignet2007hycom}), or more specifically the nested high resolution model FKEYS-HYCOM, that covers the Florida Straits, South Florida and Keys with a $\sim$900 m resolution \citep{kourafalou2012florida}. This model is embedded within the coarser GoM-HYCOM, that models the whole GoM and Florida Straits using data assimilation with a resolution of $\sim$3.5 km \citep{cummings2005operational,prasad2007upper}. However as a structured-grid model, the finer resolution of HYCOM is limited by computational resources and the nested grid approach lacks the flexibility required to adapt to the complex topology of coastal regions \citep{fringer2019future}. In contrast, unstructured-mesh models offer a well-suited solution to capture the multi-scale nature of flow features in the FRT in a computationally tractable way. They allow to locally refine the model resolution to $\sim~100$ m close to reefs and island while covering a domain large enough to capture the impact of the FC \citep{lambrechts2008multi,frys2020fine}.

@@

At the beginning of this thesis, SLIM was not able to represent wave-current interactions under storm conditions. Heavy winds generate large wind-waves that disturb ocean conditions and interact non-linearly with the currents \citep{liu2020impacts,wu2011fvcom}. The wave-generated currents cause water level variations near shorelines and wave breaking points which, in turn, affect the motion and evolution of the waves \citep{longuet1970longshore, sikiric2013coupling}. Capturing wave-current interactions hence requires the calculation of the full directional wave spectrum in order to correctly reproduce the dynamics of wind-driven surface waves. This is usually achieved by spectral wave models, which describe the evolution of the wave energy spectrum. An objective of this thesis was therefore the coupling of SLIM with the spectral wave model Simulating WAve Nearshore (SWAN, \citealp{booij1999third}), specifically developed for coastal applications and relies on numerical schemes adapted to small-scale, shallow water regions. Further details on the models and their coupling is given in chapter \ref{chap:irma}.

\section*{Outline}
This thesis is mainly a collection of publications describing our answers to the four main research questions. Chapter \ref{chap:sctld} describes the development of a coupled epidemio-hydrodynamic model to reproduce the observed spread of SCTLD in the FRT. Chapter \ref{chap:drto} explains how this model was used to study the apparent stalling of the spread of the SCTLD between the Marquesas and the DRTO. Chapter \ref{chap:onset} investigates the impact of the PMDDP on the onset of the SCTLD oubreak in 2014. Chapter \ref{chap:irma} describes the development of a coupled wave-current model to study the impacts of Hurricane Irma (2017) on wave-induced transport processes in the Florida Keys. Finally, chapter \ref{chap:conclusion} presents the conclusions of this thesis and perspectives for further works.

>>>>

Coral reefs are among the most productive and biologically diverse ecosystems on Earth \citep{connell1978diversity, moberg1999ecological}. They supply food, income and coastal protection to vast numbers of people (Fig. \ref{intro:corals}). While they account for less than 0.5\% of the ocean floor \citep{spalding1997new}, they are home for almost a third of the marine biodiversity \citep{moberg1999ecological}. Reef-related fisheries account to up to 40\% of the total marine
fish landed value of some regions \citep{teh2013global} and hundreds of millions of people depend on coral reefs for their livelihood or part of their protein intake \citep{salvat1992coral,hoegh2019people}. Through calcification, corals are the backbone of a complex three-dimensional habitat that serves as spawning, breeding and feeding area for many species \citep{moberg1999ecological,rogers2014vulnerability}. This complex reef framework  dissipates most of incoming waves energy, protects shorelines from storms and floods, and prevents coastal erosion \citep{ferrario2014effectiveness,elliff2017coral}. Additionally, wave dissipation creates lagoons and sedimentary environments, providing favorable conditions for the growth of seagrass and mangrove ecosystems \citep{moberg1999ecological,guannel2016power}.

@@

The calcifying process of reef building corals heavily depends on their symbiosis with the microalgae zooxanthellae. These unicellular symbionts convert sunlight and carbon dioxide into organic carbon and oxygen, providing the corals with most of the energy needed to meet their metabolic demands \citep{muscatine1977reef}. However, adverse environmental conditions such as elevated sea surface temperature can cause damage to the mechanisms maintaining this association, resulting in the expulsion of the endosymbionts \citep{hoegh2007coral,van2022global}. This process, called bleaching, causes the coral to loose their pigmentation and reveals their underlying white skeleton \citep{baker2008climate}. Bleached corals are then physiologically and nutritionally compromised, and prolonged bleaching over several months leads to high coral mortality \citep{hughes2018spatial}. Decline in coral health and cover pushes the reef ecosystem to a macroalgal-dominated state \citep{hughes2003climate,mumby2007thresholds}. Once a "tipping point" is exceeded, returning to a coral-dominated state becomes difficult \citep{mumby2007thresholds,graham2015predicting}.

Despite their importance, coral reefs have experienced a massive system-wide decline: it is estimated  that 50\% have already been severely damaged \citep{hoegh2019people}, and almost all could be lost under a 1.5$^\circ$C warming \citep{dixon2022future}. This global decline in live coral cover \citep{gardner2003long,pandolfi2003global,pandolfi2011projecting,perry2013caribbean,dietzel2021population} (Fig. \ref{intro:cover}) is caused by both global and local anthropogenic stressors. The main global stressors are climate change induced ocean warming and acidification \citep{dove2020ocean,figueiredo2021global,dixon2022future}. Ocean warming causes recurrent mass bleaching events at an increasing frequency \citep{connell199730, hughes2018spatial,van2022global}. Furthermore, thermal stress can increase the susceptibility of corals to disease, leading to an increase in the incidence of coral disease outbreaks \citep{harvell2002climate,bruno2007thermal,muller2012caribbean,howells2020annual}. Moreover, the increase of the concentration of atmospheric carbon dioxyde causes a decrease of the pH and carbonate concentration of seawater. As a result, coral calcification and growth decrease, which inhibits their capacity to build structurally complex habitats \citep{hoegh2007coral,albright2016reversal}. Local stressors are numerous and include pollution \citep{loya1980effects,van2011chemical}, coastal development and the associated sediment and wastewater fluxes \citep{erftemeijer2012environmental, jones2015effects,jones2019sediment,cunning2019extensive}, nutrient run-off \citep{hughes2003climate,fabricius2005effects}, and overfishing of herbivorous species controlling algae growth \citep{jackson2001historical,shantz2020overfishing}.

@@

Due to the combined damages from of all these stressors, it is almost impossible to return reefs to their past configurations \citep{hughes2017coral}. Instead, the challenge is now to maintain the biological functions of coral reefs through quickly changing environmental conditions. This will require to rapidly address greenhouse gas emissions, as well as local actions to boost the capacity of coral reef ecosystems to survive climate change \citep{hughes2003climate,knowlton2008shifting,graham2015predicting,kleypas2021designing}. The aim of the present dissertation was therefore to use modeling tools to better understand the drivers of coral demise and hence inform such local actions to support the management of Florida's Coral Reef, the third largest barrier reef of the world.

@@

The Florida Reef Tract (FRT) spans over approximately 577 km from the Dry Tortugas (DRTO), west of the Florida Keys, to the St. Lucie Inlet in Martin County, constituting the third largest barrier reef in the world \citep{finkl2008shelf} (Fig. \ref{intro:frt}). These reefs harbor a rich Caribbean fauna, including more than 40 species of stony corals \citep{banks2008reef,jackson2014status}. The northern half-section of the FRT consists of relic, Holocene framework reefs and indurated sand ridges, divided into three shore-parallel reefs (inner, middle, outer) separated by sandy plains. Benthic cover is generally denser on the middle and outer reefs while the inner reef harbors some large patches of dense \textit{Acropora cervicornis}. The dominant reef builder is the bouldering \textit{Montastraea cavernosa} but living hard coral cover is fairly low (below 3\%)\citep{banks2008reef,walton2018impacts}. The southern half-section is a chain of limestone islands (the Keys), that extends from the southern tip of the Florida mainland southwest to the DRTO on the boundary of the West Florida Shelf (WFS). The Upper Keys are remnants of ancient coral reefs and the Lower Keys are sand bars \citep{hoffmeister1968geology}. The DRTO are made of small circular reef banks whose coral populations are among the most preserved of the continental United States \citep{hine2008coral, kourafalou2018physical}. Moreover, they are believed to be important sources of recruitment for coral-reef fishes in the Florida Keys \citep{domeier2004potential}.

@@

Florida's Coral Reef (FCR) is of considerable importance to the economy of the state. \cite{johns2003socio} estimated the contribution of recreational users of natural and artificial reefs over the period June 2000 to May 2001 to have been US\$2.3 billions in sales and US\$1.1 billion in income. Moreover, recreational use of the reefs was evaluated to bring 36,500 full and part-time jobs. Focusing on natural reefs only, \cite{brander2013total} estimated the total coral reef values of Florida to be US\$174 millions. However, this value might be strongly underestimated as non-use and indirect use values, such as support for coastal fisheries \citep{ault2006building} and coastal protection \citep{ferrario2014effectiveness} were not taken into account.

Nevertheless, FCR has been heavily impacted by the human activities of the major metropolitan area of greater Miami. These impacts include densely populated coastlines, large numbers of visitors, polluted terrestrial run-off and overfishing \citep{jackson2014status}. For example, dredging operations during the PortMiami Deep Dredge Project (PMDDP) was reported to have caused the death of $>$560,000 corals \citep{cunning2019extensive}. Florida's coral reefs have therefore declined significantly over the past decades due to anthropogenic stressors and numerous disease outbreaks \citep{gardner2003long, jackson2014status,walton2018impacts}. Populations of previously dominant reef-building acroporids almost totally disappeared throughout the Caribbean and Florida \citep{aronson2001white}, and coral cover dropped from 40 to 60\% in 1975 to $<$7\% in the Florida Keys \citep{jackson2014status} and $<$3\% in the northern section of the FRT \citep{walton2018impacts}. Furthermore, since 2014, many coral species have experienced widespread and severe decline caused by the ongoing outbreak of stony coral tissue loss disease (SCTLD). For instance, populations of \textit{M. cavernosa}, once one of the most abundant species of the FRT, decreased by 45\% in abundance between 2015 and 2016 \citep{walton2018impacts}.

@@

The aforementioned large-scale ocean circulation significantly impacts transport processes in the FRT. The modeling tools developed in this thesis should therefore be able to capture them accurately. Furthermore, as our objective is to model the dispersal of disease agents and sediments in a topologically complex coastal reef ecosystem, our modeling framework should also be able to capture small-scale ocean circulation features. For instance, small-scale flow features such as recirculation eddies around reefs and islands have been shown to strongly influence larval dispersal by increasing their local retention over the reefs \citep{figueiredo2013synthesizing}. Furthermore, accurately capturing the topography of coastal areas is critical when modeling storm conditions, as large wind waves generate strong currents, waves and storm surges in nearshore regions \citep{dietrich2010high, weisberg2006hurricane}. A reference ocean model of the FRT is the 3D HYbrid Coordinate Ocean Model (HYCOM, \citealp{chassignet2007hycom}), or more specifically the nested high resolution model FKEYS-HYCOM, that covers the Florida Straits, South Florida and Keys with a $\sim$900 m resolution \citep{kourafalou2012florida}. This model is embedded within the coarser GOM-HYCOM, that models the whole GoM and Florida Straits using data assimilation with a resolution of $\sim$3.5 km \citep{cummings2005operational,prasad2007upper}. However as a structured-grid model, the finer resolution of HYCOM is limited by computational resources and the nested grid approach lacks the flexibility required to adapt to the complex topology of coastal regions \citep{fringer2019future}. In contrast, unstructured-mesh models offer a well-suited solution to capture the multi-scale nature of flow features in the FRT in a computationally tractable way. They allow to locally refine the model resolution to $\sim~100$ m close to reefs and island while covering a domain large enough to capture the impact of the FC \citep{lambrechts2008multi,frys2020fine}.

@@

At the beginning of this thesis, SLIM was not able to represent wave-current interactions under storm conditions. Heavy winds generate large wind-waves that disturb ocean conditions and interact non-linearly with the currents \citep{liu2020impacts,wu2011fvcom}. The wave-generated currents cause water level variations near shorelines and wave breaking points which, in turn, affect the motion and evolution of the waves \citep{longuet1970longshore, sikiric2013coupling}. Capturing wave-current interactions hence requires the calculation of the full directional wave spectrum in order to correctly reproduce the dynamics of wind-driven surface waves. This is usually achieved by spectral wave models, which describe the evolution of the wave energy spectrum. An objective of this thesis was therefore the coupling of SLIM with the spectral wave model Simulating WAve Nearshore (SWAN, \citealp{booij1999third}), specifically developed for coastal applications and relying on numerical schemes adapted to small-scale, shallow water regions. Further details on the models and their coupling is given in chapter \ref{chap:irma}.

\section*{Outline}
This thesis is mainly a collection of publications describing our answers to our four main research questions. Chapter \ref{chap:sctld} describes the development of a coupled epidemio-hydrodynamic model to reproduce the observed spread of SCTLD in the FRT. Chapter \ref{chap:drto} explains how this model was used to study the apparent stalling of the spread of the SCTLD between the Marquesas and the DRTO. Chapter \ref{chap:onset} investigates the impact of the PMDDP on the onset of the SCTLD oubreak in 2014. Chapter \ref{chap:irma} describes the development of a coupled wave-current model to study the impacts of Hurricane Irma (2017) on wave-induced transport processes in the Florida Keys. Finally, chapter \ref{chap:conclusion} presents the conclusions of this thesis and perspectives for further works.

### 2022-02-15 chapters/irma/article.tex
chapter on drto added to thesis
relecture II

The main questions we want to answer are the following: (1) How important are wave-current interactions during a tropical cyclone? (2) What effect do they have on the transport of drifting material? We tackle these issues by investigating the transport of drifting particles on the Florida shelf during Hurricane Irma, one of the strongest and costliest tropical cyclones on record in the Atlantic Basin \citep{xian2018brief}, which made landfall in Florida in September 2017. To do that, we developed an unstructured-mesh coupled wave-current model of the whole FRT to simulate the ocean circulation under hurricane conditions. Both modeled currents and waves were validated against field measurements and then used to simulate the transport of drifting material in the Florida Keys and over the Florida inner shelf. Model outputs were then compared with uncoupled simulation results in order to assess the impact of the radiation stress gradient and Stokes drift on the modeled currents and transport.

@@

\subsection{Wave model}
Waves were modeled using the parallel unstructured-mesh version of the Simulating WAves Nearshore (SWAN) model \citep{booij1999third}, one of the most popular wave models for coastal areas and inland waters. It solves the action balance equation \citep{mei1989applied}:
\begin{equation}
    \dfrac{\partial N}{\partial t} + \nabla_\mathbf{x}\cdot[(\mathbf{c}_g+\mathbf{u})N] + \dfrac{\partial }{\partial \theta}[c_\theta N] + \dfrac{\partial}{\partial \sigma}[c_\sigma N] = \dfrac{S_{in}+S_{ds}+S_{nl}}{\sigma}~, \label{eq:swan}
\end{equation}
where $N=E/\sigma$ is the wave action density and $E$ is the wave energy spectrum; $\theta$ is the wave propagation direction; $\sigma$ is the intrinsic wave frequency; $\mathbf{c}_g$ is the wave group velocity, $\mathbf{u}=\mathbf{U}/H$ is SLIM depth-averaged current velocity; $c_\theta$ and $c_\sigma$ are the propagation velocities in spectral space due to refraction and shifting in frequency due to variations in depth and currents; and $S_{in}$, $S_{ds}$, and $S_{nl}$ respectively represent wave growth by wind, wave decay and nonlinear transfers of wave energy through four and three-wave interactions, \ie quadruplets and triplets. The wave spectra were discretized with 48 direction bins and 50 frequency bins logarithmically distributed from 0.03 to 2 Hz. Exponential wind growth was parameterized using the formulation of \cite{janssen1991quasi}, while dissipations by whitecapping and bottom dissipation followed the formulations of \cite{komen1984existence} and \cite{madsen1989spectral}, respectively.

@@

SLIM's governing equations are integrated using an implicit time integration scheme while SWAN is unconditionally stable \citep{dietrich2012performance}, allowing both models to be run with relatively large time steps. In this study, the stationary version of SWAN was used, \ie the first term of Eq. (\ref{eq:swan}) was set to zero. This resulted in reduced scaling and convergence rates than with the nonstationary version of SWAN but increased the model stability. The wave spectra at each node of the mesh was saved at the end of each iteration to serve as initial conditions for the next one. Both models were run sequentially using a time step of 600 s, so that each computational core was alternatively running either SLIM or SWAN. As in the coupling between SWAN and the ADvanced CIRCulation model (ADCIRC) \citep{dietrich2012performance}, both models use the same local sub-mesh, allowing for a one-to-one correspondence between the geographic locations of the mesh vertices. No interpolation is therefore needed when passing the discretised variables from one model to the other, which allows an efficient inter-model communication. However, as SLIM is based on  a discontinuous Galerkin finite element method, an additional conversion step to a continuous framework was required to transfer SLIM nodal quantities to SWAN. The coupling increases the computation time by 3\% as compared to the sum of the uncoupled SLIM and SWAN simulations wall-clock times for the same number of CPUs and the same simulation period.
%The coupling increased the computation time by 400\% and 25\% respectively compared to uncoupled SLIM and SWAN model runs with the same number of CPUs over the same simulated period.

>>>>

The main questions we want to answer in this study are the following: (1) How important are wave-current interactions during a tropical cyclone? (2) What effect do they have on the transport of drifting material? We tackle these issues by investigating the transport of drifting particles on the Florida shelf during Hurricane Irma, one of the strongest and costliest tropical cyclones on record in the Atlantic Basin \citep{xian2018brief}, which made landfall in Florida in September 2017. To do that, we developed an unstructured-mesh coupled wave-current model of the whole FRT to simulate the ocean circulation under hurricane conditions. Both modeled currents and waves were validated against field measurements and then used to simulate the transport of drifting material in the Florida Keys and over the Florida inner shelf. Model outputs were then compared with uncoupled simulation results in order to assess the impact of the radiation stress gradient and Stokes drift on the modeled currents and transport.

@@

\subsection{Wave model}
Waves were modeled using the parallel unstructured-mesh version of the Simulating WAves Nearshore (SWAN) model \citep{booij1999third}, one of the most popular wave models for coastal areas and inland waters. It solves the action balance equation \citep{mei1989applied}:
\begin{equation}
    \dfrac{\partial N}{\partial t} + \nabla_\mathbf{x}\cdot[(\mathbf{c}_g+\mathbf{u})N] + \dfrac{\partial }{\partial \theta}[c_\theta N] + \dfrac{\partial}{\partial \sigma}[c_\sigma N] = \dfrac{S_{in}+S_{ds}+S_{nl}}{\sigma}~, \label{eq:swan}
\end{equation}
where $N=E/\sigma$ is the wave action density and $E$ is the wave energy spectrum; $\theta$ is the wave propagation direction; $\sigma$ is the intrinsic wave frequency; $\mathbf{c}_g$ is the wave group velocity, $\mathbf{u}=\mathbf{U}/H$ is SLIM depth-averaged current velocity; $c_\theta$ and $c_\sigma$ are the propagation velocities in spectral space due to refraction and shifting in frequency due to variations in depth and currents; and $S_{in}$, $S_{ds}$, and $S_{nl}$ respectively represent wave growth by wind, wave decay and nonlinear transfers of wave energy through four and three-wave interactions, \ie~quadruplets and triplets. The wave spectra were discretized with 48 direction bins and 50 frequency bins logarithmically distributed from 0.03 to 2 Hz. Exponential wind growth was parameterized using the formulation of \cite{janssen1991quasi}, while dissipations by whitecapping and bottom dissipation followed the formulations of \cite{komen1984existence} and \cite{madsen1989spectral}, respectively.

@@

SLIM's governing equations are integrated using an implicit time integration scheme while SWAN is unconditionally stable \citep{dietrich2012performance}, allowing both models to be run with relatively large time steps. In this study, the stationary version of SWAN was used, \ie~the first term of Eq. (\ref{eq:swan}) was set to zero. This resulted in reduced scaling and convergence rates than with the nonstationary version of SWAN but increased the model stability. The wave spectra at each node of the mesh was saved at the end of each iteration to serve as initial conditions for the next one. Both models were run sequentially using a time step of 600 s, so that each computational core was alternatively running either SLIM or SWAN. As in the coupling between SWAN and the ADvanced CIRCulation model (ADCIRC) \citep{dietrich2012performance}, both models use the same local sub-mesh, allowing for a one-to-one correspondence between the geographic locations of the mesh vertices. No interpolation is therefore needed when passing the discretised variables from one model to the other, which allows an efficient inter-model communication. However, as SLIM is based on  a discontinuous Galerkin finite element method, an additional conversion step to a continuous framework was required to transfer SLIM nodal quantities to SWAN. The coupling increases the computation time by 3\% as compared to the sum of the uncoupled SLIM and SWAN simulations wall-clock times for the same number of CPUs and the same simulation period.
%The coupling increased the computation time by 400\% and 25\% respectively compared to uncoupled SLIM and SWAN model runs with the same number of CPUs over the same simulated period.
